Self-Supervised Learning of Generalized Policies in adversarial domains

### 2021-05-28 doc/paper/paper.tex
improve in doc

\subsection{Space Invaders - v0}
\subsubsection{Description}
In this domain the agent can shoot, move to the right or to the left. The agent $A$ has two actions per turn and the mastians $m$ one. To win the agent has to kill all the martians, for this he must shoot each of them. The agent kills an opponent if he shoots while being in the same column, and he can only kill one for each shoot. The martians has three possible actions, left, right and down, all the adversaries move in the same direction. The agent cannot be destroyed by the opponents. The agent can select a Martian as a target $M$.

\subsubsection{Training instances:}
\begin{Verbatim}[fontsize=\footnotesize]
  #m...m#
  #m...M#
  #.....#
  #...A.#
\end{Verbatim}

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
(A) Num[cell-has-martian] [k=1]
(B) Bool[cell-has-target_martian] [k=1]
(C) Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]
\end{Verbatim}

\subsubsection{Feature Descrition}
$A$. Number of martians\\
$B$. There is some target martian\\
$C$. Absolute horizontal distance between agent and target martian

\subsubsection{Policy}
\begin{Verbatim}[fontsize=\footnotesize]
    1. B>0 AND C>0 -> {A ·, B ·, C ↓}
    2. A=0 AND B>0 AND C=0 -> {A ·, B ↓, C ↑}
    3. A>0 AND B>0 AND C=0 -> {A ↓, B ·}
\end{Verbatim}

\subsubsection{Policy Description}
According to the first rule if the distance between the agent and the target martian is greater than zero, it is good to decrease this distance, i.e. move towards the target martian. The third rule is applicable when there are several Martians and the agent is in the same column as the targeted Martian, and indicates that in this abstraction of the state it is good to decrease the number of Martians. The second rule indicates that if there is only one Martian left, and we are below him, it is good to eliminate him.

@@

\subsection{Space Invaders - v1}
\subsubsection{Description}
In this domain the agent $A$ can move to the right or to the left. The agent has two actions per turn and the martians $m$ have one. To win the agent has to kill all the martians, for this he must shoot each of them. The agent kills an opponent if he moves into the column of the adversary, and he can only kill one for each shoot. The adversary has three possible actions, left, right and down, and all the adversaries move in the same direction. The agent cannot be destroyed by the opponents. The agent can select a Martian as a target $M$.

\subsubsection{Training instances:}
\begin{Verbatim}[fontsize=\footnotesize]
  #m...m#
  #m...M#
  #.....#
  #...A.#
\end{Verbatim}

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  (A) Num[cell-has-martian] [k=1]
  (B) Bool[cell-has-target_martian] [k=1]
  (C) Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]
  absolute horizontal distance between agent and target martian
\end{Verbatim}

\subsubsection{Feature Descrition}
$A$. Number of martians\\
$B$. There is some target martian\\
$C$. Absolute horizontal distance between agent and target martian

\subsubsection{Policy}
\begin{Verbatim}[fontsize=\footnotesize]
  1. B>0 AND C=0 -> {A ·, B ·, C ↑}
  2. B>0 AND C>0 -> {A ·, B ·, C ↓}
  3. A=0 AND B>0 AND C>0 -> {A ·, B ↓}
  4. A>0 AND B>0 AND C>0 -> {A ↓, B ·}
\end{Verbatim}

\subsubsection{Policy Description}
In the $Space Invaders - v1$ the agent cannot shoot, but he can kill the Martians by positioning himself in their column. According to the second rule, if the agent is not in the column of the target Martian, it is good to move closer to this column. According to the first rule of the policy, if we are below the target Martian, it is good to increase the horizontal distance between him and the agent. Intuitively, if the agent is under the target Martian, it is good to for the agent to moves away from the target martinan and then get in his column and finish him off. Finally, rules three and four say that transitions to states where the number of Martians has decreased are good.

\subsubsection{Example of Game}
\begin{Verbatim}[fontsize=\footnotesize]
  m..m # m..M # m..M # .... # .... # .... # .... # .... # .... # .... # .... # .... #
  m..M # m... # m... # m..M # m... # m... # .m.. # .M.. # .M.. # M... # M... # .... #
  .... # .... # .... # m... # M... # M... # .M.. # .... # .... # .... # .... # .... #
  .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... #
  ..A. # ...A # ..A. # ..A. # ...A # ..A. # ..A. # .A.. # ..A. # ..A. # .A.. # A... #
\end{Verbatim}

@@

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  (A) Bool[And(col-has-AGENT,col-has-TARGET)] [k=3]
  (B) Bool[And(col-has-AGENT,Exists(adjacent_col,col-has-TARGET))] [k=5]
  (C) Dist[row-has-TARGET;adjacent_row;row-has-AGENT] [k=4]
\end{Verbatim}

@@

@@

\subsubsection{Policy}
\begin{Verbatim}[fontsize=\footnotesize]
  1. A=0 AND B=0 AND C>0 AND D>0 -> {A ·, B ↑, C ↑, D ↓}, {A ↑, B ·, C ↓, D ↑},
                                    {A ↑, B ·, C ↓, D ↓}, {A ·, B ·, C ↓, D ↓},
                                    {A ·, B ↑, C ↓, D ↓}

>>>>

\subsection{Space Invaders - v0}
\subsubsection{Description}
In this domain the agent can $shoot$, move to the $right$ or to the $left$. The agent during his turn can do two actions, while the Martians can do one. Note that if the Martians and the agent have only one action per turn the agent cannot win, this is because of the situation where the agent stands in the Martian's column to shoot him on his next turn, but the next turn (the Martian's turn) the Martian can move away, this leads to an infinite loop if both are playing perfectly. That is, the agent must be able to move to the agent's column and then shoot. To win the agent has to kill all the martians, for this he must shoot each of them. The agent kills an opponent if he shoots while being in the same column, and he can only kill one for each shoot. The martians has three possible actions $left$, $right$, $up$ and $down$. All the adversaries move in the same direction. The agent cannot be destroyed in any way by the Martians, they can go down to the row above the agent. The agent cannot collide with the Martians as they cannot descend to the row above it. Note that the policy found is optimal and will solve all possible instances of the game. The policy is also optimal for a version of the game where the Martians destroy the agent when they reach the row above him.

\subsubsection{Training instances:}
\begin{Verbatim}[fontsize=\footnotesize]
  # m  .  .  m #
  # m  .  .  m #
  # .  .  .  . #
  # .  .  .  . #
  # .  .  .  . #
  # .  .  A  . #
\end{Verbatim}

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
(A) Num[cell-has-martian] [k=1]
(B) Dist[col-has-agent;adjacent_col;col-has-martian] [k=4]
\end{Verbatim}

\subsubsection{Feature Descrition}
$A$. Number of martians\\
$B$. Minimum absolute horizontal distance between a column with an agent and a column with martian

\subsubsection{Policy}
\begin{Verbatim}[fontsize=\footnotesize]
  1. A>0 AND B>0 -> {A ·, B ↓}
  2. A>0 AND B=0 -> {A ↓}
\end{Verbatim}

\subsubsection{Policy Description}
According to the first rule if the agent is not in the column of a Martian, $B$ is greater than zero, it is good to decrement $B$, i.e. move towards the closest martian. The second rule is applicable when the agent is under a Martian, in the same column, and according to this rule it is good to decrease the number of Martians, i.e. execute the action $shoot$.

@@

@@

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  (A) Bool[And(col-has-agent,col-has-adversary)] [k=3]
  (B) Bool[And(col-has-agent,Exists(adjacent_col,col-has-adversary))] [k=5]
  (C) Dist[row-has-agent;adjacent_row;row-has-adversary] [k=4]
\end{Verbatim}

\subsubsection{Feature Description}
$A$. The agent and the adversary are in the same column\\
$B$. The agent column is adjacent to the adversary column\\
$C$. Absolute vertical distance between the agent and the adversary

@@

\subsubsection{Policy Description}

@@

\subsubsection{Policy}
\begin{Verbatim}[fontsize=\footnotesize]
  1. A=0 AND B=0 AND C>0 AND D>0 -> {A ·, B ↑, C ↑, D ↓},
                                    {A ↑, B ·, C ↓, D ↑},
                                    {A ↑, B ·, C ↓, D ↓},
                                    {A ·, B ·, C ↓, D ↓},
                                    {A ·, B ↑, C ↓, D ↓}
\end{Verbatim}
